---
title: "ex1"
output: html_document
date: "2023-05-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(reshape2)
library(plotly)
library(caret)
library(readr)
library(ggplot2)
library(tidyr)
library(forcats)
library(partykit)
library(randomForest)
library(pdp)
library(ggpubr)
```

# Exercise 5.- Model-agnostic: Partial Dependency Plot (PDP).


```{r}
day <- read.csv2("day.csv", header = T,  sep = ",")
data1 <- day['season']
data1$season <- as.factor(data1$season)
dummy <- dummyVars(" ~ .", data=data1)
newdata <- data.frame(predict(dummy, newdata = data1))
data2 <- cbind(day, newdata)

apply <- function(x) {
  ifelse(x == 2, 1, 0)
}
data2$MISTY = apply(data2$weathersit)

apply2 <- function(x) {
  ifelse(x == 3 | x == 4, 1, 0)
}

data2$RAIN <- apply2(data2$weathersit)

denorm <- function(x, mini, maxi){
  x <- x*(maxi-mini)+mini
}

data2$temp <- as.numeric(data2$temp)
data2$hum <- as.numeric(data2$hum)
data2$windspeed <- as.numeric(data2$windspeed)

data2$temp <- denorm(data2$temp, -8, 39)
data2$hum <- data2$hum*100
data2$windspeed <- data2$windspeed*67

data2$dteday <- as.Date(data2$dteday, format='%Y-%m-%d')

data2$days_since_2011 <- as.integer(data2$dteday - as.Date('2011-01-01',format='%Y-%m-%d'))
```


##1.- One dimensional Partial Dependence Plot.

EXERCISE:
Apply PDP to the regression example of predicting bike rentals. Fit a random forest approximation for the prediction of bike rentals (cnt). Use the partial dependence plot to visualize the relationships the model learned. Use the slides shown in class as model.  

```{r}
rf <- randomForest( data = data2, cnt~. , ntrees = 500)
pdp.days <-partial(rf, pred.var = c("days_since_2011"), chull = TRUE)
plot.days <- autoplot(pdp.days, contour = TRUE) + ylim(3000,5000)+ ylab('Predicted number of bikes')
pdp.temp <-partial(rf, pred.var = c("temp"), chull = TRUE)
plot.temp <- autoplot(pdp.temp, contour = TRUE) + ylab('') + ylim(3000,5000)
pdp.hum <-partial(rf, pred.var = c("hum"), chull = TRUE)
plot.hum <- autoplot(pdp.hum, contour = TRUE) + ylab('Predicted number of bikes') + ylim(3000,5000)
pdp.ws <-partial(rf, pred.var = c("windspeed"), chull = TRUE)
plot.ws <- autoplot(pdp.ws, contour = TRUE) + ylab('') + ylim(3000,5000)
ggarrange(plot.days, plot.temp, plot.hum, plot.ws, nrow = 2, ncol = 2)
```

QUESTION:
Analyse the influence of days since 2011, temperature, humidity and wind speed on the predicted bike counts.

The influence of the variable 'days_since_2011' has 3 different levels. Firstly, when the variable is lower than 100, the number of bikes is around 4250, once the variable getst
