---
title: "ex2"
output: html_document
date: "2023-05-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(reshape2)
library(plotly)
library(caret)
library(readr)
library(ggplot2)
library(tidyr)
library(forcats)
library(partykit)
library(randomForest)
library(pdp)
library(ggpubr)
```

# Exercise 5.- Model-agnostic: Partial Dependency Plot (PDP).


```{r}
day <- read.csv2("day.csv", header = T,  sep = ",")
data1 <- day['season']
data1$season <- as.factor(data1$season)
dummy <- dummyVars(" ~ .", data=data1)
newdata <- data.frame(predict(dummy, newdata = data1))
data2 <- cbind(day, newdata)

apply <- function(x) {
  ifelse(x == 2, 1, 0)
}
data2$MISTY = apply(data2$weathersit)

apply2 <- function(x) {
  ifelse(x == 3 | x == 4, 1, 0)
}

data2$RAIN <- apply2(data2$weathersit)

denorm <- function(x, mini, maxi){
  x <- x*(maxi-mini)+mini
}

data2$temp <- as.numeric(data2$temp)
data2$hum <- as.numeric(data2$hum)
data2$windspeed <- as.numeric(data2$windspeed)

data2$temp <- denorm(data2$temp, -8, 39)
data2$hum <- data2$hum*100
data2$windspeed <- data2$windspeed*67

data2$dteday <- as.Date(data2$dteday, format='%Y-%m-%d')

data2$days_since_2011 <- as.integer(data2$dteday - as.Date('2011-01-01',format='%Y-%m-%d'))

```

## 2.- Bidimensionl Partial Dependency Plot

EXERCISE:
Generate a 2D Partial Dependency Plot with humidity and temperature to predict the number of bikes rented depending on those parameters.

```{r}
set.seed(56)
random.length  <-  sample(x = 200:500, size = 1)
subset <- data2[sample(nrow(data2), random.length), ]

rf <- randomForest( data = subset, cnt~. , ntrees = 500)

bi_pdp <-pdp::partial(rf, pred.var =c("temp",'hum'), train = subset)

p <- ggplot(bi_pdp, aes(x = temp, y = hum))+geom_tile(aes(fill= yhat))
p 
```

QUESTION:
Interpret the results
The following graph comes to show how the effect that the humidity has over the number of rented bikes is not comparable to the one that the temperature has, meaning that we clearly see a significant change in the number of bikes when changing temperature, this change most significant when the temperature goes from 13 to 15. Whereas there is no significant increase or decrease in the rented bikes has the humidity is higher or lower.